Exercising choice over feedback schedules during practice is not advantageous for motor learning

### 2022-08-22 docs/preprint/supplementary.tex
update: preprint and supplementary versions

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\usepackage{csquotes}
\usepackage{pdflscape}
\usepackage{setspace}
\raggedbottom
\AtBeginDocument{\let\maketitle\relax}
\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Exercising choice over feedback schedules during practice is not advantageous for motor learning},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\caption{\small \onehalfspacing \textbf{Post-test (collapsed across retention and transfer) timing E (ms) shift function.} The top row illustrates scatter plots of individual mean timing E for each group in Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}. The middle row illustrates the same scatter plots as the top row, but with the deciles of each distribution represented by the black lines. The thick black line represents the the median of each distribution. The deciles from each group are joined by colored lines, with blue (Experiment 1) and green (Experiment 2) indicating lower error for the choice group deciles, and red (Experiment 1) and green (Experiment 2) indicating lower error for the yoked group deciles. The bottom row illustrates the shift function, which focuses on the grey shaded region of the x-axis in the middle row. The deciles for the choice group are plotted on the x-axis and the difference in deciles between the choice and yoked group are plotted on the y-axis. The vertical dash line represents the median of the choice distribution. The same color coding for differences in deciles from the middle row is used in the bottom row. Error bars represent 95\% confidence intervals, corrected for multiple comparisons. The horizontal dashed line represents zero differences between the deciles of the two group. If a 95\% confidence interval overlaps with zero, there is no significant difference between the two groups on that decile of the distribution. There were no significant differences for any decile in either experiment.}\label{fig:figS4}
\end{figure}

\newpage

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\usepackage{csquotes}
\usepackage{setspace}
\raggedbottom
\AtBeginDocument{\let\maketitle\relax}
\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Exercising choice over feedback schedules during practice is not advantageous for motor learning},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\caption{\small \normalfont \onehalfspacing \textbf{Total timing error estimation data.} Boxplots of retention and transfer data from all participants for Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}. The Choice with error feedback (Choice+Error) group is shown in dark blue, the Choice with graded feedback (Choice+Graded) group is shown in light blue, the Choice with binary feedback (Choice+Binary) group is shown in green, the Yoked with error feedback (Yoked+Error) group is shown in red, the Yoked with graded feedback (Yoked+Graded) group is shown in yellow, and the Yoked with binary feedback (Yoked+Binary) group is shown in purple. Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean. Grey connected dots represent individual data for participants in each group. Individual data of 1 participant in each of the Choice+Error, Yoked+Error, and Yoked+Binary groups is not shown as their error exceeded 500 ms.}\label{fig:figS4}
\end{figure}

\clearpage

\hypertarget{performance-accuracy-of-estimators-versus-non-estimators}{%
\subsection{Performance accuracy of estimators versus non-estimators}\label{performance-accuracy-of-estimators-versus-non-estimators}}

We assessed whether performance accuracy differed between the subset of participants who were randomly assigned to estimate their error in pre-test compared to those who were not. Total error for the spatial and timing goals were analyzed in separate mixed ANOVAs (\emph{Acquisition}: 2 Estimation x 6 Block; \emph{Learning}: 2 Estimation x 2 Test) for each experiment. None of the main effect or interactions were significant in Experiment 1 or Experiment 2. A possible explanation for this finding is that estimating one's error is most effective when knowledge of results feedback is provided following the estimation (Guadagnoli \& Kohl, 2001). Another possible explanation is that self-controlled feedback schedules promote spontaneous error estimation (e.g., Chiviacowsky \& Wulf, 2005). Given recent support for this idea (Bacelar et al., 2022), it seems plausible that all participants in a self-controlled group in the present experiments engaged is some form of error estimation activities throughout acquisition when they deliberated about using (or not using) one of their limited feedback requests.

\clearpage

\hypertarget{supplementary-c}{%
\section{Supplementary C}\label{supplementary-c}}

Contrary to the motivational perspective (i.e., OPTIMAL theory), we did not find that the opportunity to exercise choice over feedback during practice enhanced perceptions of competence, autonomy, or intrinsic motivation relative to not having this same choice opportunity. Equivalence tests can be used to null findings more informative (Harms \& Lakens, 2018; Lakens, 2017; Schuirmann, 1987); however, a typical two one-sided test procedure may not be appropriate for this analysis for a couple reasons. First, we did not specify an \emph{a priori} smallest effect size of interest for any of the psychological constructs. Second, the questionnaires were administered at various time points---after pre-test, after acquisition blocks 1 and 6, and before retention---during the experimental protocol. Given the choice and feedback manipulations were present at after acquisitions blocks 1 and 6 and not after pre-test or before retention, it would be inappropriate to aggregate across time points. We instead report mean differences and 90\% confidence intervals between choice and yoked groups at each questionnaire time point for both experiments. The present experiments can be considered inconsistent with all effects larger than \(g = \pm\) the largest absolute confidence interval bound presented in Table \ref{tab:tableS1}.

\vspace{1em}

\begin{table}[h!]

\caption{\label{tab:tableS1}Effect sizes for each questionnaire at each timepoint.}
\resizebox{\linewidth}{!}{
\fontsize{11}{13}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{11em}>{\raggedright\arraybackslash}p{2em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{2em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{2em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{2em}>{\raggedright\arraybackslash}p{5em}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{After pre-test} & \multicolumn{2}{c}{After block 1} & \multicolumn{2}{c}{After block 6} & \multicolumn{2}{c}{Before retention} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9}
Questionnaire & $g$ & 90\% CI & $g$ & 90\% CI & $g$ & 90\% CI & $g$ & 90\% CI\\
\midrule
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Experiment 1}}\\
\hspace{1em}Perceived autonomy & .10 & {}[-.17, .36] & .22 & {}[-.05, .49] & .32 & {}[.05, .59] & .28 & {}[.01, .55]\\
\hspace{1em}Perceived competence & .07 & {}[-.19, .34] & .10 & {}[-.17, .36] & -.12 & {}[-.38, .15] & -.11 & {}[-.37, .16]\\
\hspace{1em}Intrinsic motivation & .27 & {}[0, .54] & .20 & {}[-.07, .46] & .17 & {}[-.09, .44] & .15 & {}[-.11, .42]\\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Experiment 2}}\\
\hspace{1em}Perceived autonomy & -.02 & {}[-.29, .24] & .12 & {}[-.15, .39] & .15 & {}[-.11, .42] & -.03 & {}[-.30, .23]\\
\hspace{1em}Perceived competence & .12 & {}[-.15, .38] & -.08 & {}[-.35, .18] & .22 & {}[-.05, .49] & .10 & {}[-.16, .37]\\
\hspace{1em}Intrinsic motivation & -.31 & {}[-.58, -.04] & -.22 & {}[-.48, .05] & -.20 & {}[-.46, .07] & -.17 & {}[-.43, .10]\\
\bottomrule
\multicolumn{9}{l}{\rule{0pt}{1em}\textit{Note.} Block 1 and 6 are from the acquisition phase. Negative values favor yoked group.}\\
\end{tabular}}
\end{table}

\clearpage
